%% -*- coding: utf-8; -*-

\documentclass[master,american]{ThesisPUC}

%%
%%Text and Figure formatting packages
%%

%% \usepackage[brazilian]{babel}      %% in ThesisPUC.cls
%% \usepackage[utf8]{inputenc}        %% .
%% \usepackage[T1]{fontenc}           %% .
%% \usepackage{lmodern}               %% .
%% \usepackage[pdftex]{graphicx}	%% .

%\usepackage[framemethod=tikz]{mdframed}

%\usepackage[%
%dvipsnames,
%svgnames,
%x11names,
%fixpdftex
%]{xcolor} %Lists of colors to use in the text

\usepackage{float}

%%
%%Mathematics symbols packages
%%
\usepackage{amsmath, esint}
\usepackage{amssymb}
\usepackage{empheq}


%%
%% Add inkscape figures with extension .pdf_tex
%%
\usepackage{import}
\usepackage{xifthen}
\usepackage{pdfpages}
\usepackage{transparent}

%%
%% Table packages
%%

\usepackage{tabularx}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{booktabs}


%%
%% Miscellaneous
%%

\usepackage{numprint} %Prints numbers with thousand separator
\usepackage{textcomp} %Text Companion fonts
\usepackage{enumitem} %Control layout of itemize & enumerate
\usepackage[numbers]{natbib} %Organizar numeração da bibliografia

%\usepackage{tikz}

% \usepackage{etoolbox}

%% numprint 
\npthousandsep{.}
\npdecimalsign{,}

%% ThesisPUC option
%% \tablesmode{figtab} %% [nada, fig, tab ou figtab]

%%%
%%% Counters
%%%

%% uncomment and change for other depth values
%% \setcounter{tocdepth}{3}
%% \setcounter{lofdepth}{3}
%% \setcounter{lotdepth}{3}
%% \setcounter{secnumdepth}{3}


%%%
%%% New commands and other global definitions
%%%

\input{defs}

%%%
%%% Misc.
%%%

\usecolour{true}

%%%
%%% Titulos
%%%

\author{Alexandre Augusto Abreu Almeida}
\authorR{Abreu Almeida, Alexandre Augusto}

\advisor{Celia Beatriz Anteneodo de Porto}{Profa.}
\advisorR{Anteneodo, Celia}

\title{Estudo de um modelo simples para um diodo térmico}

\titleuk{Study of a simple model for a thermal diode}

%% \subtitulo{Aqui vai o subtitulo caso precise}

\day{15}
\month{April}
\year{2020}

\city{Rio de Janeiro}
\CDD{620.11} %??????
\department{Física}
\program{Física } %???????
\school{Centro Técnico Científico} %???????
\university{Pontifícia Universidade Católica do Rio de Janeiro}
\uni{PUC-Rio }

%%%
%%% Jury
%%%

\jury{%
  \jurymember{Fulano}{Prof.}
    {????}{????}
  \jurymember{Fulana}{Profa.}
    {????}{????}
  \jurymember{Fulano de tal}{Prof.}
    {????}{????}
  \jurymember{Fulena}{Profa.}
    {????}{????}
  \schoolhead{José Eugenio Leal}{Prof.}
}


%%%
%%% Resume
%%%

\resume{%
  Majored in Chemical Engineering by Universidade Federal do Rio de Janeiro - UFRJ (Rio de Janeiro, Brazil).
}


%%%
%%% Acknowledgment
%%%

\acknowledgment{%
  \noindent I would like to first thank my advisor ...
  \bigskip

  \noindent Then I wish to thank ...
}


%%%
%%% Catalog prekeywords
%%%

\catalogprekeywords{%
  \catalogprekey{Physics}% 
}


%%%
%%% Keywords
%%%

\keywords{%
  \key{Condução Térmica;}
  \key{Lei de Fourier;}
  \key{Oscilador;}
  \key{Cadeia de Osciladores;}
}

\keywordsuk{%
  \key{Thermal Conduction;}
  \key{Fourier's Law;}
  \key{Oscillator;}
  \key{Chain of Oscillators;}
}


%%%
%%% Abstract
%%%

\abstract{%
	Nós simulamos a lei de fourier da condução de calor por meio de um modelo consistindo em uma cadeia de osciladores e mostramos que com algumas pequenas mudanças esse modelo pode descrever os chamados diodos térmicos.
}

\abstractuk{%
	We simulate fourier's law of heat conduction by means of a model consisting of a chain os oscillators and then show that with a few small changes this model can describe the so called thermal diodes.
}

%%%
%%% Dedication
%%%

\dedication{%
  dedication.
}

%%%
%%% Epigraph
%%%

\epigraph{%
  My beautifull epigraph
}
\epigraphauthor{Alguém}
\epigraphbook{Algum livro}


%%%
%%%
%%%


\begin{document}

  \input{abrevs}
  \input{chapter-1}
  \input{chapter-2}
  \input{chapter-3}
  \input{chapter-4}
  \input{conclusions}
  %% ...
  \arial
  \nocite{*}
  \bibliography{thesis_alexandre}
  \normalfont
  \input{appendix}

\end{document}
